Project-I by Group ROME

### 2015-10-31 report/paper.tex

\documentclass{article} % For LaTeX2

@@

We performed featurewise analysis to notice that most of our real valued
variables have nearly gaussian distributions (or at least unimodal
distributions), which is not the case of our output variable. Figure
\ref{fig:cor1} shows how the output variable evolves as a function of the first
feature. This behaviour is what we notice on most variables, and thus shows no
clear correlations.
\end{document}

>>>>

<<<<<<< HEAD
\documentclass{article} % For LaTeX2

@@

We performed featurewise analysis to notice that most of our real valued
variables have nearly gaussian distributions (or at least unimodal
distributions), which is not the case of our output variable. Figure
\ref{fig:cor1} shows how the output variable evolves as a function of the first
feature. This behaviour is what we notice on most variables, and thus shows no
clear correlations.
\end{document}
=======
\documentclass{article} % For LaTeX2e
% We will use NIPS submission format
\usepackage{nips13submit_e,times}
% for hyperlinks
\usepackage{hyperref}
\usepackage{url}
% For figures
\usepackage{graphicx} 
\usepackage{subfigure} 
% math packages
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsopn}
\usepackage{ifthen}
\usepackage{natbib}

\title{Project-I by Group CITYNAME}

For our first attempt at predicting the data, we simply used the initial
features and used kFold with $k=4$ to display the evolution of the RMSE as a
function of the regularizing lambda both for the training and test data. 
The lambda we used ranged from $10^{-4}$ to
$10^3$, with 500 points. The results of the ridge regression are already
satisfactory, with an error of approximately $0.32\pm0.005$ on the training set
and $0.34\pm0.005$ on the test set, that is approximately one third of the
standard deviation of the output variable.

The results described here are summerized in the Figure \ref{fig:ridgeCurve}.

\subsection{Feature transformations}
As notified in a previous section, among all the feature at our disposal,
features 49 and 66 show distributions that ressemble the ditribution of the
output variable.

This led us to try and regress only on thos two features and polynomial
transformations of them. Using only those two features, we get an RMSE error
that is quite close to the one we notified when all the features are used. When
using polynomial features (up to degree 10), we basically get half the error
that we got using all the features. Those results were obtained using ridge
regression. As in the previous section, we obtained the RMSE as a function of
lambda, calculating both training and test errors using a kFold procedure with
$k=4$. The results are summarized in Figure \ref{fig:polyridgeCurve}, where, as
previously mentionned, we used as features only the two features and their
polynomial transformation with degree ranging from 1 to 10.

As expected, both training error and test error decrease as the proportion of
training data increases. The test error obtained seems to exhibit a quite
satisfactory behaviour.

\subsection{Regression Summary}
While simple ridge regression with an appropriately optimized lambda already
gave decent results on our dataset, we obtained better results using polynomial
transformations of well chosen features. Doing so, we obtain an error that is
approximately one fifth of the standard deviation.

\end{document}
>>>>>>> cad465af211561b5f7c07cebe323918cf8ff2cfd
